Modelling the Trojan Asteroids

### 2020-04-24 Report/draft1.tex
Complete planet_mass_variation

\lettrineabstract{Trojan asteroids are v important. I'm going to make that paragraph a little longer to fill out the space in case this is forming some kind of error. i really hope this is long enough.}

@@

The overall wander, however, is observed to follow Fig \ref{fig:zwander}.
It is suggested that, while the maximum deviation from the Lagrange point in the z direction is simply twice the initial perturbation, wander in the xy plane increases quadratically. This can be initiated from a radial displacement due to the reduced gravitational force  under the z perturbation, demonstrated in Fig \ref{fig:zorbit}, or more significantly from an initial perturbation in the xy plane.

@@

\begin{figure}
	\centering
	\includegraphics[width=0.8\linewidth]{Figures/wanderwithplanetmass_p5b}
	\caption{Variation of maximum wander with planetary mass, under a 0.01 AU radial perturbation and 0.01 AU/year tangential boost. Note the well defined quadratic trend up to $ M_{p} = 0.026 M_{s}$, and instability beyond this.}
	\label{fig:planetmass}
\end{figure}

A quadratic trend (with a large quadratic component) is initially observed, but wander deviates from this at approximately $ M_{p} = 0.026 M_{s}$, with a sharp increase indicating orbit instability. This occurs significantly before the theoretical prediction of $ M_{p} = 0.04 M_{s}$ \cite{Darwin1897}, however it is suggested this is due to instabilities in the integration solver.

>>>>

\lettrineabstract{Trojan asteroids are v important. I'm going to make that paragraph a little longer to fill out the space in case this is forming some kind of error. i really hope this is long enough. Word Count: XXXX}

@@

The overall wander, however, is observed to follow Fig \ref{fig:zwander}.
It is suggested that, while the maximum deviation from the Lagrange point in the z direction is simply twice the initial perturbation, wander in the xy plane increases quadratically. This can be initiated from a radial displacement due to the reduced gravitational force  under the z perturbation, demonstrated in Fig \ref{fig:zorbit}, or more significantly from an initial perturbation in the xy plane. However, the oscillation of gravitational forces due to perturbations in the z direction make this problem significantly more complicated and likely result in the observed deviations from the quadratic relations.

@@

\begin{figure}
	\centering
	\includegraphics[width=0.8\linewidth]{Figures/wanderwithplanetmass_p6}
	\caption{Variation of maximum wander with planetary mass, under a 0.01 AU radial perturbation and 0.01 AU/year tangential boost. Note the orbit stability up to $ M_{p} = 0.04 M_{s}$, and instability beyond this.}
	\label{fig:planetmass}
\end{figure}

An approximate quadratic trend is initially observed in the small mass region, with minimum wander occurring at $ M_{p} = 0.026 M_{s}$. However the variation of wander below $ M_{p} = 0.04 M_{s}$ in minimal, while orbits are unstable beyond this point, in agreement with theoretical predictions by Darwin \cite{Darwin1897}.
